HerMES: ALMA Imaging of {\it Herschel}$^{\dagger}$-selected Dusty Star-forming Galaxies

### 2015-04-22 LaTeX/ms.tex
Deleted unnecessary figures.

The starting point for the sample selection is source extraction and
photometry.  For the objects in this paper, individual catalogs were generated
for each of the 250$\, \mu$m, 350$\,\mu$m, and 500$\,\mu$m {\it Herschel}
Spectral and Photometric Imaging REceiver \citep[SPIRE;][]{2010A&A...518L...3G}
channels using the SUSSEXtractor peak finder algorithm \citep{Savage:2007sf}.
Our sample includes 29 DSFGs drawn from five independent, confusion-limited
fields in HerMES with declinations $< 2 ^\circ$ and totaling $55\,$deg$^2$.

@@

\bibitem[{{Griffin} {et~al.}(2010)}]{2010A&A...518L...3G}
{Griffin}, M.~J. {et~al.} 2010, \aap, 518, L3+

>>>>

The starting point for the sample selection is source extraction and
photometry.  For the objects in this paper, individual catalogs were generated
for each of the 250$\, \mu$m, 350$\,\mu$m, and 500$\,\mu$m {\it Herschel}
Spectral and Photometric Imaging REceiver \citep[SPIRE;][]{Griffin:2010lr}
channels using the SUSSEXtractor peak finder algorithm \citep{Savage:2007sf}.
Our sample includes 29 DSFGs drawn from five independent, confusion-limited
fields in HerMES with declinations $< 2 ^\circ$ and totaling $55\,$deg$^2$.

@@

\bibitem[{{Griffin} {et~al.}(2010)}]{Griffin:2010lr}
{Griffin}, M.~J. {et~al.} 2010, \aap, 518, L3+
